\primarybold{Einarr Rasmussen (Level 6)}

\primary{Male Human Slayer 6}

\alignmentage{NG}{Medium Humanoid (Human)}{49}

\initsense{+5}{Perception +13}

\labelcategory{ᛉ}{Defence}

\ac{19 [20]}{15}{14 [15]}

\secondaryindent{(+5 Dex, +4 Armour, [+1 Shield])}

\hpsavetable{43}{6d10 + 0}{10 + 6 + 10 + 2 + 9 + 6}{Fort  &  +5  &  +5  &  +0  \\  Ref  &  +10  &  +5  &  +5  \\  Will  &  +4  &  +2  &  +2}

\labelcategory{ᛏ}{Offence}

\speedcarry{30 ft.}{58/116/175 lbs.}

\attacktable{Melee}{mwk Battle Axe [+6 BAB +2 Str + 1 Enh]}{Normal  &  +9/+5  &  1d8 + 2/x3  &    \\  Two-handed  &  +8/+4  &  1d8 + 3/x3  &  (−1 AC, buckler)}

\attacktable{Ranged}{+1 Composite (+2 Str) shortbow [+6 BAB +5 Str + 1 Enh]}{Normal  &  +12/+7  &  1d6 + 3/x3  &    \\  Deadly Aim  &  +10/+5  &  1d8 + 7/x3  &    \\  Rapid Shot  &  +10/+10/+5  &  1d8 + 3/x3  &    \\  R. Shot + D. Aim  &  +8/ +8/+3  &  1d8 + 7/x3  &  }

\secondaryheader{Special Attacks}{Point-blank shot (+1/+1), Sneak Attack (+2d6), Studied Target (+2 atck/dam, +2 to DCs)}

\labelcategory{ᚾ}{Statistics}

\abilityscoretable{}{Str  &  +2  &  14  &  15  &  −1 (age)  \\  Dex  &  +5  &  20  &  18  &  −1 (age) +2 (race) + 1 (lvl)  \\  Con  &  +0  &  10  &  11  &  −1 (age)  \\  Int  &  +2  &  15  &  14  &  −1 (age)  \\  Wis  &  +2  &  14  &  13  &  −1 (age)  \\  Cha  &  +0  &  10  &  9  &  −1 (age)}

\babcmbcmd{+6}{+8}{23}

\secondaryheader{Languages}{Dvårgs, Rhäns, Aquitains}

\labelcategory{ᚦ}{Feats [3 + 3b]}

\quasitable{1}{Deadly Aim}{Until the end of next turn: −2 on all ranged attack rolls, +4 on ranged damage rolls.}

\quasitable{1b}{Alertness}{+2 to perception and sense motive.}

\quasitable{2b}{Precise Shot}{Shoot into melee without the standard −4 penalty.}

\quasitable{3}{Point Blank Shot}{+1 on attack and damage rolls with all ranged weapons within 30 ft.}

\quasitable{5}{Rapid Shot}{When making a full-attack, fire an extra arrow at your highest bonus. All attacks are made at a −2 penalty.}

\quasitable{6b}{Improved Precise Shot}{Ranged attacks ignore the AC bonus and miss chance granted by anything less than total cover or total concealment.}

\labelcategory{ᚦ}{Skills [9 + class skill/level]}

\skilltable{}{ᛋ  &  Acrobatics  &  +12  &  4  &  +3  &  +5  &    \\    &  Bluff*  &  +9  &  6  &  +3  &  +0  &    \\    &  Climb  &  +11  &  6  &  +3  &  +2  &    \\  ᛋ  &  Craft (Fletcher)  &  +6  &  1  &  +3  &  +2  &    \\  ᛋ  &  Heal  &  +6  &  1  &  +3  &  +2  &    \\  ᛒ  &  Knowledge* (loc)  &  +9  &  4  &  +3  &  +2  &    \\    &  Knowledge* (geo)  &  +11  &  6  &  +3  &  +2  &    \\  ᛒ  &  Knowledge* (nob)  &  +7  &  2  &  +3  &  +2  &    \\    &  Perception*  &  +13  &  6  &  +3  &  +2  &  +2(feat)  \\  ᛗ  &  Profession (Courier)  &  +7  &  2  &  +3  &  +2  &    \\  ᛗ  &  Ride  &  +10  &  2  &  +3  &  +5  &    \\    &  Sense Motive*  &  +13  &  6  &  +3  &  +2  &  +2(feat)  \\    &  Stealth  &  +19  &  6  &  +3  &  +5  &  +5(compt)  \\    &  Survival*  &  +11  &  6  &  +3  &  +2  &  +3(track)  \\  ᛗ  &  Swim  &  +7  &  2  &  +3  &  +2  &  }

\secondaryindent{*Studied Target (2/+2)}

\labelcategorybreak{ᛈ}{Slayer Abilities}

\specialabilityfreq{Studied Target}{ex}{2 targets / +2}{Study opponent as a move action (or immediate action after sneak attack). Gain +2 [untyped] bonus on Bluff, Knowledge, Perception, Sense Motive, Survival, Weapon Attack and Damage rolls against it. Lasts until target is dead or a new target is selected. Max 2 targets.}

\specialability{Track}{ex}{+3 on survival skill checks made to follow tracks.}

\specialability{Sneak Attack}{ex}{+2d6 on denied Dex to AC or Flank.}

\labelcategory{ᚻ}{Slayer Talents [3]}

\specialability{Ranger Combat Style}{Ex}{Precise Shot (Archery)}

\specialability{Fast Stealth}{Ex}{Move at full speed when using stealth.}

\specialability{Ranger Combat Style}{Ex}{Improved Precise Shot (Archery)}

\labelcategory{ᛟ}{Special Gear}

\secondaryheader{+1 Composite (+2 str) Shortbow}{martial, ranged, piercing; CL 3, faint evocation; 2 lbs.}

\secondaryheader{Mwk Battleaxe}{martial, one handed, slashing; 6 lbs.}

\secondaryheader{Mwk Buckler}{You can use a bow or crossbow without penalty while carrying it. You can use two-handed attacks, but you incur a −1 penalty on attack rolls and lose the AC bonus until your next turn.; — max dex, 0 ACP, 5\% ASF.}

\secondaryheader{Saðrsilfr Shirt}{light armour; +4 armour bonus; 10 lbs.; +6 max dex, 0 ACP, 10\% ASF.}

\secondaryheader{Cloak of Álfrkind}{+5 competence bonus on stealth checks when worn with hood up; shoulder slot, CL 4, faint illusion; 1 lbs.}

\secondaryheader{Ullr's Quiver}{Can contain up to 20 + 60 arrows, 18 javalins and 6 bow/spears etc. Can produce any item as if from a regular quiver or scabbard.; slotless, CL 9, moderate conjuration.}

\secondaryheader{Boots of the Cat}{always take minumum possible falling damage, and always land on your feet.; feet slot, CL 1, faint transmutation.}

\secondaryheader{Quick Runner's Shirt}{(1/day) as a swift action take an additional move action to move and immediately end your turn.; chest slot, CL 5, faint transmutation; --lbs.}

\labelcategory{ᚠ}{Inventory}

\invtable{}{8 Daggers (1 per boot, 6 in belts)  &  16 gp  &  8 lbs.  \\  mwk Battleaxe  &  310 gp  &  6 lbs.  \\  mwk Buckler  &  155 gp  &  5 lbs.  \\  +1 Composite (+2 str) Shortbow  &  2,525 gp  &  2 lbs.  \\  Silk Rope (50 ft.)  &  10 gp  &  5 lbs.  \\  Saðrsilfr Shirt  &  1,100 gp  &  10 lbs.  \\  Cloak of Álfrkind  &  2,500 gp  &  1 lbs.  \\  Boots of the Cat  &  1,000 gp  &  1 lbs.  \\  Quick Runner's Shirt  &  1,000 gp  &  — lbs.  \\  Ullr's Quiver  &  1,800 gp  &  2 lbs.  \\  Bjørnsten Ring  &  ~365 gp  &  — lbs.  \\  ASsorted Survival Gear  &  ~100 gp  &  10 lbs}

\invtable{Ullr's Quiver (1st compartement)}{60 arrows  &  3 gp  &  9 lbs.}

\invtable{Ullr's Quiver (2nd compartement)}{60 cold iron arrows  &  6 gp  &  9 lbs.  \\  20 silver arrows  &  41 gp  &  3 lbs.  \\  3 adamantine arrows  &  180 gp  &  — lbs.  \\  4 shortbows  &  120 gp  &  8 lbs.}

\invtable{Ullr's Quiver (1st compartement)}{2 Longbows  &  150 gp  &  6 lbs.  \\  4 Spears  &  8 gp  &  24 lbs.}

